Supplementary Materials

### 2021-10-11 analysis/supplementary-materials/supp-mat.Rmd
AGH second revisions to first draft

```{r setup, include=FALSE}
library(here)
library(tidyverse)
raw_data <- read_csv(here("analysis/data/raw_data/starch_counts.csv"))
```

@@

@@

```{r}
raw_data %>%
  filter(treatment == "control") %>%
  select(!c(vol, portion_slide, s, m, l))
```

>>>>

```{r setup, include=FALSE}
library(here)
library(tidyverse)
raw_data_samples <- read_csv(here("analysis/data/raw_data/starch_counts.csv"))
raw_data_solutions <- read_csv(here("analysis/data/raw_data/solution_counts.csv"))
```

@@

## Raw data

Raw counts from the treatment solutions before extrapolation.

```{r raw-data-sol, echo=FALSE}
raw_data_solutions
```

Raw counts from the calculus samples before extrapolation:

```{r raw-data-samp, echo=FALSE}
raw_data_samples
```

The raw data can be downloaded from GitHub:

```sh
# solution counts
wget https://github.com/bbartholdy/byoc-starch/blob/main/analysis/data/raw_data/solution_counts.csv

# sample counts
wget https://github.com/bbartholdy/byoc-starch/blob/main/analysis/data/raw_data/starch_counts.csv
```

@@

```{r}
raw_data_samples %>%
  filter(treatment == "control") %>%
  select(!c(vol, portion_slide, s, m, l))
```
